On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-07 MS.tex

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the model fits did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4} d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

>>>>

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4} d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.
